Tree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-21 manuscript/climate_sensitivity_draft.Rmd
discussion

Our study reveals that tree height, microhabitat, and species' hydraulic traits interactively shape tree growth responses to drought.

@@

7. science is better
- by advancing our understanding of the mechanisms for individual-level responses to drought, this opens door for better predictions (elaborate from above). "This is absolutely critical to predicting forest responses to future droughts, which we're likely to see more of in the future as a result to climate change. Forecasting forest responses to these droughts is a huge and important challenge",
- furthermore, we have deepened understading of which trees will suffer , and there are implications.
- big trees

>>>>

As climate change drives increasing drought in many of the world's forests (*REFS*), the fate of forests and their climate feedbacks will be shaped by the biophysical and physiological drivers observed here. Tall trees with exposed crowns are suffering disroportionately,

@@

7. science is better
- by advancing our understanding of the mechanisms for individual-level responses to drought, this opens door for better predictions (elaborate from above). "This is absolutely critical to predicting forest responses to future droughts, which we're likely to see more of in the future as a result to climate change. Forecasting forest responses to these droughts is a huge and important challenge",
- furthermore, we have deepened understading of which trees will suffer , and there are implications.
- big trees
- traits/ successional status?
